formula1

### 2020-06-07 inst/f1points.Rmd
typos

```{r,montecarlofirst,cache=TRUE}
top <- 11
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))

## Now work on synthetic dataset generation:
points1 <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points2 <- c(1, 0,0,0,0)
resampling <- function(m,f2017,points){
    random_table <- rrank(n=ncol(f2017), p=m)
    rownames(random_table) <- colnames(f2017)
    ## "random_table" is a random table; now calculate lstar and pstar for
    ## likelihood ranks and points ranks respectively:

@@

    p_star <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),p)
    p_star <- sort(p_star,decreasing=TRUE)
    p_star[] <- seq_along(p_star)

    goodness <- sum(cumprod(names(p_star)==names(l_star)))
    return(goodness)
}

@@

table(o1)
table(o2)

```

>>>>

```{r,montecarlosetup, echo=FALSE, cache=FALSE}
top <- 11
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
#m <- maxp(ordertable2supp(as.ordertable(f2017)))

## Now work on synthetic dataset generation:
resampling <- function(m,f2017,points){
    random_table <- rrank(n=ncol(f2017), p=m)
    rownames(random_table) <- colnames(f2017)
    ## "random_table" is a random table; now calculate lstar and pstar for
    ## likelihood ranks and points ranks respectively:

@@

    p_star <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),points)
    p_star <- sort(p_star,decreasing=TRUE)
    p_star[] <- seq_along(p_star)

    goodness <- sum(cumprod(names(p_star)==names(l_star)))
    return(goodness)
}
```

Now

```{r,montecarlosetup2, cache=TRUE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))

points1 <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points2 <- c(1, 0,0,0,0)

@@

table(o1)
table(o2)
```
